CIVILITY: Cloud based Interactive Visualization of Tractography Brain Connectome

### 2016-07-12 doc/spiePaper/article.tex
DOC : spie pape : abstract less than 200 words
DOC : add links to github and nitrc pages

CIVILITY performs the brain connectivity analysis in remote computing grids where the CIVILITY-tractography pipeline is deployed. CIVILITY uses clusterpost\footnote{https://github.com/NIRALUser/clusterpost} to submit the jobs to the computing grid. Clusterpost is a server application providing a REST api to submit jobs in remote computing grids using. Data transfer, job execution and monitoring are all handled by clusterpost.
The front end of CIVILITY submits tasks to clusterpost and retrieves results when they are finished.
This work is motivated by medical applications in which brain connectivities need to be computed automatically and analyzed easily.

@@

In this paper, we present CIVILITY, an open source web application hosted in a cloud. This tool offers to researchers the possibility to launch a unique tractography script and to visualize the brain connectome interactively. Each user is identified by a user account associated with privileges and can access to his results from anywhere in the cloud.
The tractography pipeline uses the probabilistic method  of tractography\footnote{describe all possible trajectories} using surfaces as seeds (FSL tools : bedpostx and probtrackx). The tractography pipeline is executed on the computing grid and once is finished results are retrieved and brain connectome visualization is available. 
The graphic visualization of the brain connectome is generated using Data Driven Documents (D3.js) and more precisely the method Hierarchical Edge Bundling. This is a circle plotting representing the brain connectivity. All links can be threshold between two values, their shape can also be modified for an easier visualization. This tool is submitted at the SPIE Medical Imaging 2016 conference in the category Image processing and we seek to enable further clinical and research applications of tractography.

@@

This section explains in details the two components of CIVILITY : tractography and visualization.

@@

The entire pipeline is available in the github project repository.

>>>>

CIVILITY performs the brain connectivity analysis in remote computing grids where the CIVILITY-tractography pipeline is deployed. CIVILITY uses clusterpost\footnote{https://github.com/NIRALUser/clusterpost} to submit the jobs to the computing grid. 
%Clusterpost is a server application providing a REST api to submit jobs in remote computing grids using. Data transfer, job execution and monitoring are all handled by clusterpost.
The front end of CIVILITY submits tasks to clusterpost and retrieves results when they are finished.
This work is motivated by medical applications in which brain connectivities need to be computed automatically and analyzed easily.

@@

In this paper, we present CIVILITY an open source web application hosted in a cloud. This tool offers to researchers the possibility to launch a unique tractography script and to visualize the brain connectome interactively. Each user is identified by a user account associated with privileges and can access to his results from anywhere in the cloud.
The tractography pipeline uses the probabilistic method  of tractography\footnote{describe all possible trajectories} using surfaces as seeds (FSL tools : bedpostx and probtrackx). The tractography pipeline is executed on the computing grid and once is finished results are retrieved and brain connectome visualization is available. 
The graphic visualization of the brain connectome is generated using Data Driven Documents (D3.js) and more precisely the method Hierarchical Edge Bundling. This is a circle plotting representing the brain connectivity. All links can be threshold between two values, their shape can also be modified for an easier visualization. This tool is submitted at the SPIE Medical Imaging 2016 conference in the category Image processing and we seek to enable further clinical and research applications of tractography.

@@

This section explains in details the two components of CIVILITY : tractography and visualization.
The figure \ref{fig:architectureCIVILITY} shows the architecture of the application CIVILITY.

\begin{figure}
\centering 
\subfigure[]{\includegraphics[width=15cm]{architectureCIVILITY.png}}
\caption[Architecture of the application CIVILITY]{Architecture of the application CIVILITY}
\label{fig:architectureCIVILITY}
\end{figure}

@@

The entire pipeline is available in the github project repository\footnote{https://github.com/NIRALUser/CIVILITY} or in the NITRC page\footnote{https://www.nitrc.org/projects/civility/}.
